---
title: "Get Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{get_started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

# globe4r::shared_background("#060606")
```

This document will let you get started with globe4r. First, install the library from github using either the [remotes](https://github.com/r-lib/remotes) or the [devtools](https://github.com/r-lib/devtools) packages.

```r
# install remotes if you do not have it already
install.packages("remotes")

# install globe4r
remotes::install_github("JohnCoene/globe4r")
```

Once installed, you can load the package.

```{r setup}
library(globe4r)
```

## Your First Globe

Every globe will be initiated with the `create_globe` function.

```{r}
create_globe()
```

You can use any background you want for globe using the `globe_img_url` function; as indicated by the function name these must be served on a server (i.e.: the `www` forlder of a [Shiny](https://shiny.rstudio.com/) app). The `image_url` function provides easy access to four popular such backgrounds, you can also use any from the [echarts4r.assets](https://cdn.jsdelivr.net/gh/JohnCoene/echarts4r.assets/inst/assets/) package. 

With a globe drawn we can pipe (`%>%`) various data layers:

1. bars
2. arcs
3. polygons
4. points

The above can be added via two different APIs, a convenient ggplot2-like API and raw API matching the underlayong JavaScript library one-to-one. This document covers the former.

## Coords

The package makes use of `coords` (coordiantes) which behaves like the `aes` function in [ggplot2](https://ggplot2.tidyverse.org/articles/ggplot2-specs.html).

```{r}
create_globe() %>% 
  globe_pov(-21, 179) %>% # position camera
  globe_bars(
    coords(lat, long), 
    data = quakes
  )
```

There are numerous coordinates (`coords`) available. 

- `lat`, `lon`
- `start_lat`, `start_lon`
- `end_lat`, `end_lon`
- `altitude`
- `radius`
- `color`
- `label`
- `resolution`
- `merge`
- `transition`
- `size`
- `text`
- `rotation`
- `include_dot`
- `dot_radius`
- `dot_orientation`
- `type_face`
- `altitude_scale`
- `stroke`
- `curve_resolution`
- `circular_resolution`
- `dash_length`
- `dash_gap`
- `dash_initial_gap`
- `dash_animate_time`
- `country`,
- `side_color`, `cap_color`

## Scales

You can use the various `scale_` functions to ensure the data is as the underlying JavaScript library expects it. For instance, `altitude` is ideally between 0 (flat) and 1 (radius of the globe).

```{r}
create_globe() %>% 
  globe_pov(-21, 179) %>% # position camera
  globe_bars(
    coords(
      lat, long, 
      altitude = depth,
      color = depth,
      label = stations # on hover label
    ), 
    data = quakes
  ) %>% 
  scale_bars_color() %>% 
  scale_bars_altitude()
```