---
title: "Polygons"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{polygons}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(globe4r)
```

By default the `globe_choropleth` function will plot `data` against an internal database of country polygons. Below use a globe4r dataset to plot the percentage of agricultural land available per country.

```{r}
data(agriland)

create_globe(height = "100vh") %>% 
  globe_choropleth(
    coords(
      country = country_code,
      altitude = percent,
      cap_color = percent
    ), 
    data = agriland
  ) %>% 
  scale_choropleth_cap_color() %>%  
  scale_choropleth_altitude(0.06, 0.1) 
```

However one is not limited to use those polygons. The latter are defined by GeoJSON which can easily be obtained in R.

1. First use the `raster` package to fetch the desired map (shapefile).
2. You are advsied to use `rmapshaper` to simplify the map as it will make it load much faster in the browser.
3. Finally use `geojsonio` to convert the file to GeoJSON

All of the packages above are available on CRAN.

<details>
<summary>Install.</summary>
<p>
```r
pkgs <- c("raster", "rmapshaper", "geojsonio")
install.packages(pkgs)
```
</p>
</details>

```{r}
# get shapefile
india_sp <- raster::getData('GADM', country = 'INDIA', level = 1)

# optionally reduce its size (strongly recommended)
india_small <- rmapshaper::ms_simplify(india_sp, keep = 0.05) 

# convert to JSON
india_geojson <- geojsonio::geojson_list(india_small)
```

Now we can build mock data to plot against our mock GeoJON. We can fetch the name of each polygon using the `NAME_` + `level` formula, or `NAME_1` in our case, this can be found under `properties`.

```{r}
regions <- india_geojson$features %>% 
  purrr::map("properties") %>% 
  purrr::map("NAME_1") %>% 
  unlist()

mock_data <- data.frame(
  NAME_1 = regions,
  value = runif(length(regions), 1, 100)
)

mock_data %>% 
  head() %>% 
  knitr::kable()
```

Note that the we also use `NAME_1` in our data, this will be used internally to match data to their respective polygons.

```{r}
create_globe() %>% 
  globe_choropleth(
    data = mock_data,
    coords(
      polygon = NAME_1,
      cap_color = value
    ),
    polygons = india_geojson
  ) %>% 
  globe_pov(19, 77, 1) %>% 
  scale_choropleth_cap_color()
```
